--- 
title: Layers descriptions 
output: 
  html_document: 
    toc: true 
    toc_depth: 1 
    number_sections: false 
    toc_float: yes 
---

```{r, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE} 
 library(tidyverse) 
 library(knitr) 
 
 layer_meta <- readr::read_csv('https://raw.githubusercontent.com/OHI-Science/mhi/master/prep/data_layers.csv') 
 layer_path <- 'https://github.com/OHI-Science/mhi/tree/master/region2017/layers' 
 
 
```

 
# access 
####[ao_access](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/ao_access_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/ao_access.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# aquarium fishing 
####[fp_fish_aquarium](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fp_aquarium_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fp_fish_aquarium.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# area of active fishponds 
####[mar_fishpond_current](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/mar_fishpond_current_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/mar_fishpond_current.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# area within 1 km of the shore 
####[lsp_area_1km_coast](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/lsp_area_1km_coast_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/lsp_area_1km_coast.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# artisanal fisheries management effectiveness and opportunity 
####[fp_mora_artisanal](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fp_mora_artisanal_gl2016.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fp_mora_artisanal.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# average visitors per day 
####[t_average_visitors](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/t_average_visitors_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/t_average_visitors.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# beach condition 
####[hab_health_mhi](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hab_health_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hab_health_mhi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# beach extent 
####[hab_extent_mhi](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hab_extent_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hab_extent_mhi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# beach trend 
####[hab_trend_mhi](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hab_trend_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hab_trend_mhi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# biodiversity coastal wetland extent 
####[hab_extent_mhi](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hab_extent_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hab_extent_mhi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# bottom fisheries commercial catch 
####[fis_deep_catch](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fis_deep_catch_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fis_deep_catch.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# CITES signatories 
####[g_cites](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/g_cites_gl2016.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/g_cites.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# coastal conservation districts 
####[lsp_coastal_condist](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/lsp_coastal_conservation_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/lsp_coastal_condist.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# coastal MPAs fisheries resilience 
####[fp_MPA_3nm](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fp_MPA_3nm_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fp_MPA_3nm.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# coastal MPAs habitat resilience 
####[hd_MPA_3nm](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hd_MPA_3nm_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hd_MPA_3nm.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# coastal protection coastal wetland extent 
####[cp_hab_extent_mhi2017](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/cp_hab_extent_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/cp_hab_extent_mhi2017.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# coastal wetland condition 
####[hab_health_mhi](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hab_health_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hab_health_mhi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# commercial fishery hi-bycatcb 
####[fp_com_hb](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fp_com_hb_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fp_com_hb.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# commercial fishery lo-bycatcb 
####[fp_com_lb](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fp_com_lb_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fp_com_lb.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# commercial fishing management 
####[fp_mora](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fp_mora_gl2016.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fp_mora.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# commercial reef fisheries catch 
####[fis_reef_catch](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fis_reef_catch_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fis_reef_catch.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# commerical coastal pelagic fisheries catch 
####[fis_coast_pelagic_catch](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fis_coast_pelagic_updated_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fis_coast_pelagic_catch.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# community stewardship 
####[community_stewardship](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/community_stewardship_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/community_stewardship.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# competitiveness in achieving sustained economic prosperity 
####[li_gci](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/li_gci_gl2016.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/li_gci.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# coral bleaching 
####[cc_sst_nearshore](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/cc_sst_nearshore_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/cc_sst_nearshore.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# cp wetlands 
####[wetlands_coastal_1km](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/wetlands_coastal_1km) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/wetlands_coastal_1km.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# direct impacts from humans (trampling, recreation, etc) 
####[hd_tourrec_direct_h](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hd_tourrec_direct_h_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hd_tourrec_direct_h.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# economic loss from sea level rise 
####[cc_slr_eco](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/cc_slr_eco_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/cc_slr_eco.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# EEZ MPAs fisheries resilience 
####[fp_mpa_eez](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fp_MPA_eez_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fp_mpa_eez.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# EEZ MPAs habitat resilience 
####[hd_mpa_eez](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hd_MPA_eez_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hd_mpa_eez.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# EEZ protected marine areas to protect fishery resources 
####[fp_mpa_eez](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fp_mpa_eez_gl2016.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fp_mpa_eez.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# environmental protection 
####[t_env_sus](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/t_env_sus_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/t_env_sus.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# ESA coastal plant status 
####[spp_status](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/spp_status_mhi_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/spp_status.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# ESA marine mammal status 
####[spp_status](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/spp_status_mhi_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/spp_status.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# ESA seabird and coastal bird status 
####[spp_status](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/spp_status_mhi_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/spp_status.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# experience of visitors 
####[tourism_experience](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/tourism_experience_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/tourism_experience.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# fish biomass 
####[spp_fish](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/spp_fish_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/spp_fish.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# fishpond status 
####[mar_fishpond_health](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/mar_fishpond_health_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/mar_fishpond_health.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# forest/watershed health 
####[forest_health](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/forest_health_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/forest_health.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# habitat destruction caused by coastal engineering 
####[hd_coasteng](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hd_coasteng_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hd_coasteng.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# habitat destruction from dredging 
####[hd_dredging](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hd_dredging_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hd_dredging.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# habitat destruction of benthic structures 
####[hd_benstr](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hd_benstr_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hd_benstr.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# habitat health 
####[res_hab_health](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/res_hab_health_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/res_hab_health.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# habitat weights 
####[element_wts_hab_pres_abs](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/element_wts_hab_pres_abs_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/element_wts_hab_pres_abs.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# inflation adjusted usd 
####[gdp_usd](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/le_gdp_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/gdp_usd.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# invasive species (algae and mangroves) 
####[sp_ispp_a_m](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/sp_ispp_a_m_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/sp_ispp_a_m.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# land-based sediment export to nearshore water 
####[po_lbsp_sed](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/po_lbsp_sed_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/po_lbsp_sed.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# land-based source of pollution from agriculture and golf courses 
####[po_lbspaggolfrunoff](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/po_lbspaggolfrunoff_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/po_lbspaggolfrunoff.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# land-based source of pollution from urban runoff 
####[po_lbspurbanrunoff](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/po_lbspurbanrunoff_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/po_lbspurbanrunoff.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# landbased source of pollution pathogens 
####[po_lbsp_nosds_bil](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/po_lbsp_nosds_bil_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/po_lbsp_nosds_bil.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# management and protection of habitat to preserve biodiversity (fisheries) 
####[fp_habitat](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fp_habitat_gl2016.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fp_habitat.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# management of nonindigenous species 
####[sp_alien_species](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/sp_alien_species_gl2016.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/sp_alien_species.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# mariculture yield 
####[mar_harvest](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/mar_harvest_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/mar_harvest.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# marine debris 
####[po_marinedebris](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/po_marinedebris_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/po_marinedebris.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# marine managed areas 
####[lsp_mma_mhi2017](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/lsp_mma_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/lsp_mma_mhi2017.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# measure of coastal ecological integrity 
####[species_diversity_3nm](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/species_diversity_3nm_gl2016.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/species_diversity_3nm.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# Mo'omeheu - Value of History and Culture 
####[sp_OHA_culture](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/sp_OHA_culture.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/sp_OHA_culture.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# multipliers 
####[NA](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/NA) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/NA.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# number of fishponds 
####[mar_fishpond_numbers](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/mar_fishpond_numbers_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/mar_fishpond_numbers.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# ocean acidification 
####[cc_acid](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/cc_acid_gl2016.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/cc_acid.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# ocean and coastal jobs 
####[le_jobs](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/le_jobs_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/le_jobs.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# ocean and coastal revenue 
####[le_gdp](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/le_gdp_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/le_gdp.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# ocean warming 
####[cc_warm](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/cc_warm_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/cc_warm.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# offshore area to 3nm 
####[lsp_area_3nm_mhi2017](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/lsp_area_3nm_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/lsp_area_3nm_mhi2017.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# operations 
####[mar_operations](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/mar_operations_census_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/mar_operations.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# participation in recreational activities 
####[r_participation_mhi2017](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/r_participation_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/r_participation_mhi2017.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# pelagic fisheries commerical catch 
####[fis_pelagic_catch](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fis_pelagic_catch_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fis_pelagic_catch.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# percent of forest dominated by non-native species 
####[forest_health](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/forest_health_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/forest_health.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# protected marine areas within EEZ to protect against habitat destruction 
####[hd_mpa_eez](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hd_mpa_eez_gl2016.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hd_mpa_eez.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# proxy for intertidal habitat destruction 
####[hd_intertidal](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hd_intertidal_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hd_intertidal.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# recreational catch multiplier 
####[fis_reef_catch_multiplier](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fis_reef_catch_multiplier_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fis_reef_catch_multiplier.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# reef condition 
####[cp_hab_condition](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/cp_hab_condition_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/cp_hab_condition.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# reef extent 
####[hab_extent_mhi](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hab_extent_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hab_extent_mhi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# reef fishing catch 
####[fp_reeffish_t](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fp_reeffish_t_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fp_reeffish_t.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# reef trend 
####[hab_trend_mhi](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hab_trend_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hab_trend_mhi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# resident population 
####[le_popn](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/le_pop_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/le_popn.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# resident sentiment 
####[t_sentiment](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/t_sentiment_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/t_sentiment.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# resource 
####[ao_resource](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/ao_resource_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/ao_resource.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# sea level rise 
####[cc_sealevel](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/cc_sealevel_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/cc_sealevel.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# sea surface temperature 
####[cc_sst_eez](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/cc_sst_eez_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/cc_sst_eez.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# sector evenness as a measure of economic diversity 
####[li_sector_evenness](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/need to put in local data layer for this) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/li_sector_evenness.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# ship-based groundings 
####[hd_shipbased_ground](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hd_shipbased_ground_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hd_shipbased_ground.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# ship-based pollution 
####[po_shipbased_shipp](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/po_shipbased_shipp_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/po_shipbased_shipp.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# Social Progress Index 
####[res_spi](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/res_spi_gl2016.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/res_spi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# soft bottom condition 
####[hab_health_mhi](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hab_health_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hab_health_mhi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# soft bottom extent 
####[hab_extent_mhi](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hab_extent_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hab_extent_mhi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# soft bottom trend 
####[hab_trend_mhi](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hab_trend_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hab_trend_mhi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# state conservation districts 
####[lsp_coastal_condist](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/lsp_coastal_condist_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/lsp_coastal_condist.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# State New Economy Index 
####[li_economic_index](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/li_economic_index.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/li_economic_index.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# strength of governance 
####[wgi_all](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/wgi_all_gl2016.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/wgi_all.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# sustainability of bottomfishery 
####[fis_sus_score](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fis_sus_updated_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fis_sus_score.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# sustainability of pelagic fishery 
####[fis_sus_score](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fis_sus_updated_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fis_sus_score.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# sustainability of reef fishery 
####[fis_sus_score](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/fis_sus_updated_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/fis_sus_score.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# terrestrial aquaculture 
####[sp_aquacul_terrest](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/sp_aquacul_terrest_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/sp_aquacul_terrest.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# unemployment 
####[le_unemployment](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/le_unemployment_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/le_unemployment.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# uv radiation 
####[cc_uv](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/cc_uv_gl2016.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/cc_uv.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# visitor contributed GDP 
####[t_growth](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/t_growth_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/t_growth.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# visitors participating in kayaking 
####[NA](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/t_kayaking_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/NA.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# visitors participating in snorkeling or scuba diving 
####[NA](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/t_snorkel_scuba_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/NA.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# visitors participating in surfing 
####[NA](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/t_boarding_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/NA.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# visitors participating in swimming 
####[NA](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/t_swimming_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/NA.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# visitors participating in thrill craft 
####[NA](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/t_thrill_craft_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/NA.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# visitors participating in whale watching 
####[NA](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/t_whale_watching_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/NA.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# watershed partnerships 
####[watershed_partnerships](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/watershed_partnerships.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/watershed_partnerships.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# watersheds protected 
####[hd_watersheds](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hd_watersheds_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hd_watersheds.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# weakness of governance 
####[ss_wgi](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/ss_wgi_gl2016.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/ss_wgi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# weakness of social progress 
####[ss_spi](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/ss_spi_gl2016.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/ss_spi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# wetland trend 
####[hab_trend_mhi](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/hab_trend_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/hab_trend_mhi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# workforce 
####[le_wkforce](https://github.com/OHI-Science/mhi/tree/master/region2017/layers/le_wkforce_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/layers_all/le_wkforce.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
