---
title: "Preliminary OHI scores for the Main Hawaiian Islands"
output:
  html_document
#    keep_md: true
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
source("./_site.R")
```

Ocean Health Index scores are calculated for each region for each goal before being combined into an overall Index score for Hawaii. The four regions are Hawaii, Maui Nui, Oahu, and Kauai & Niihau. <!---could bring back the Regions page to be only linked from here---> 

Flower plots display preliminary scores, with each petal representing an individual goal. Petal lengths convey the score of the goal, thus longer petals are closer to achieving their target. Only goals that are relevant to a region are scored, otherwise they are set to NA with grey petals. All scores are on a scale from 0-100, and the center number is the region's Index score.

----

```{r plot_flower Casey}

## All borrowed from Casey: https://github.com/OHI-Science/ohibc/blob/master/regionHoweSound/ohibc_howesound_2016.Rmd
source('https://raw.githubusercontent.com/OHI-Science/ohibc/master/src/R/common.R')
source('https://raw.githubusercontent.com/OHI-Science/ohibc/master/regionHoweSound/plot_flower.R')


## set up for plotting
score_df <- scores %>%
  filter(dimension == 'score') %>%
  select(-region_id) %>%
  distinct() %>%
  inner_join(weight, by = 'goal')

goal_labels <- score_df %>%
  left_join(read_csv('goal_names.csv'),
            by = 'goal') %>%
  mutate(goal_label = str_replace(goal_label, ' ', '\n'),
         goal_label = paste(goal_label, round(score), sep = '\n')) %>%
  select(goal, goal_label)

## Casey's new flower plot!!
plot_obj <- plot_flower(score_df,
                        filename    = file.path('images', 'mhi_test.png'),
                        goal_labels = goal_labels, 
                        incl_legend = TRUE) 

## and plotly
### NOTE:: currently plotly doesn't work with polar coordinates https://github.com/ropensci/plotly/issues/878
# library(plotly) # devtools::install_github("ropensci/plotly")
# p <- ggplotly(plot_obj)
# p

```


[<img src="https://docs.google.com/drawings/d/1633uvIYgsBhiKBddQAaTlvYDJgOK1uiDB6wkooNyhFc/pub?w=576&h=288" width="100px">](http://ohi-science.org)  
[ohi-science.org home](http://ohi-science.org)
