---
title: "Preliminary OHI scores for the Main Hawaiian Islands"
output:
  html_document:
    toc: true
    toc_float: true
#    keep_md: true
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
source("./_site.R")
```

Ocean Health Index scores are calculated for each region for each goal before being combined into an overall Index score for Hawaii. The four regions are Hawaii, Maui Nui, Oahu, and Kauai & Niihau. <!---could bring back the Regions page to be only linked from here---> 

Flower plots display preliminary scores, with each petal representing an individual goal. Petal lengths convey the score of the goal, thus longer petals are closer to achieving their target. Only goals that are relevant to a region are scored, otherwise they are set to NA with grey petals. All scores are on a scale from 0-100, and the center number is the region's Index score.

----

```{r plot flowers for current scenario year}
redo_flowers = TRUE

# vars
png_res = 72
scores_csv  = sprintf('%s/scores.csv', dir_scenario)
goals_csv   = sprintf('%s/conf/goals.csv', dir_scenario)
regions_csv = sprintf('%s/layers/%s.csv', dir_scenario, config$layer_region_labels)

# data
scores  = read_csv(scores_csv)  # View(scores)
regions = read_csv(regions_csv) # View(regions)
goals   = read_csv(goals_csv)   # View(goals)

# prep
dir.create('images/flowers', showWarnings = F)
regions = bind_rows(
  data_frame(                # order regions to start with whole study_area
    rgn_id = 0,
    label = study_area),
  regions %>%
    arrange(label)) %>%   # followed by regions within alphabetically
  mutate(
    flower_png = sprintf('images/flower_%s.png', gsub(' ','_', label)))

# get goals for flowers, all and specific to weights
goals.all = arrange(goals, order_color)[['goal']]

# get colors for aster, based on 10 colors, but extended to all goals. subselect for goals.wts
cols.goals.all = colorRampPalette(RColorBrewer::brewer.pal(10, 'Spectral'), space='Lab')(length(goals.all))
names(cols.goals.all) = goals.all

# get subgoals and goals, not supragoals, for doing flower plot
goals_supra = na.omit(unique(goals$parent))
wts = with(
  subset(goals, !goal %in% goals_supra, c(goal, weight)), 
  setNames(weight, goal))
goal_labels = gsub('\\n', '\n', with(
  goals, setNames(name_flower, goal))[names(wts)], fixed=T)

# generate flower plots
for (rid in regions$rgn_id){ # rid = regions$rgn_id[1]

  # rgn
  r = filter(regions, rgn_id==rid)

  # skip if flower png exists and not redoing
  if (file.exists(r$flower_png) & !redo_flowers) next

  # scores
  g_x = with(
    subset(scores, dimension=='score' & region_id==rid),
    setNames(score, goal))[names(wts)]
  x   = scores %>%
    filter(dimension=='score', region_id==rid & goal == 'Index') %>%
    .$score
  
  # plot
  png(r$flower_png, width=400, height=250, res=png_res)
  par(omi=c(0,0.85,0,0.85))
  PlotFlower(
    lengths=ifelse(
      is.na(g_x),
      100,
      g_x),
    widths=wts,
    fill.col=ifelse(
      is.na(g_x),
      'grey80',
      cols.goals.all[names(wts)]),
    labels = '',
    center=round(x),
    max.length = 100, disk=0.4, label.cex=0.9, label.offset=0.155, cex=2.2, cex.main=2.5)
  dev.off()
}
```


[<img src="https://docs.google.com/drawings/d/1633uvIYgsBhiKBddQAaTlvYDJgOK1uiDB6wkooNyhFc/pub?w=576&h=288" width="100px">](http://ohi-science.org)  
[ohi-science.org home](http://ohi-science.org)
