---
title: "2018 Hawai‘i Ocean Health Index Scores"
output:
  html_document:
    toc: true
    toc_float: true
#    keep_md: true
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
source("./_site.R")
```

Ocean Health Index scores are calculated for each region for each goal before being combined into an overall Index score for the Main Hawaiian Islands. The four regions are Hawai‘i, Maui Nui, O‘ahu, and Kaua‘i & Ni‘ihau. <!---could bring back the Regions page to be only linked from here---> 

Flower plots display preliminary scores, with each petal representing an individual goal. Petal lengths convey the score of the goal, thus longer petals are closer to achieving their target. All scores are on a scale from 0-100, and the center number is the region's Index score.

For more information on how these scores are calculated see [Goals](http://ohi-science.org/mhi/goals.html) and our technical report [here]().

----

<!---
NOTE: Here the flower plots are displayed for each region and the overall assessment area (rgn_id = 0). Figures will be displayed directly from online in the reports/figures folder: to make sure you're displaying the most recent flower plots here's what to do: 
1. from the master branch, save new flower plots, and push
2. from the gh-pages branch, reknit this page or rebuild the website, and push!
--->

```{r plot_flower, results='asis'}

## regions info: order regions to start with whole study_area
regions <- bind_rows(
  data_frame(                
    region_id   = 0,
    region_name = 'Main Hawaiian Islands'),
  read_csv(sprintf('%s/spatial/regions_list.csv', dir_scenario_gh)) %>%
    select(region_id   = rgn_id,
           region_name = rgn_name))

## path for figures to display
regions <- regions %>%
  mutate(flower_png = sprintf('%s/reports/figures/flower_%s.png',
                              dir_scenario_gh,
                              stringr::str_replace_all(region_name, ' ', '')))

## display header, flower ----

cat(sprintf('## %s\n\n![](%s)\n\n\n\n', regions$region_name, regions$flower_png), 
    sep = "")

```


[<img src="https://docs.google.com/drawings/d/1633uvIYgsBhiKBddQAaTlvYDJgOK1uiDB6wkooNyhFc/pub?w=576&h=288" width="100px">](http://ohi-science.org)  
[ohi-science.org home](http://ohi-science.org)
