---
output:
  html_document:
    toc: true
    toc_float: true
---

```{r set up, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
library(tidyverse)

source(
  "https://raw.githubusercontent.com/OHI-Science/mhi/master/region2017/conf/web/join_layer_csvs.R")


## rename for rendering below
layers_csv <- layers_join

# ## check to make sure filenames all match
# check <- layers_join %>%
#   select(targets, layer, filename_conf, filename_prep) %>%
#   mutate(isequal = filename_conf == filename_prep)
# 
# ## fails our check 
# checkfails <- check %>%
#   filter(is.na(isequal) | isequal == FALSE) %>%
#   write_csv('layers_filename_fails.csv')
#   


```


## Food Provision: Fisheries

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "FIS.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets %in% "FIS") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))
```

---- 

## Food Provision: Mariculture

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "MAR.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="MAR") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))
```

---- 

## Artisanal Fishing Opportunity 

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "AO.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="AO") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))
```

---- 

---- 

## Coastal Protection

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "CP.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="CP") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))

```

---- 

## Sustainable Tourism

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "TR.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="TR") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))

```

---- 

## Livelihoods & Economies: Livelihoods

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "LIV.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="LIV") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))

```


---- 

## Livelihoods & Economies: Economies

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "ECO.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="ECO") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))
```

---- 

## Sense of Place: Connection to Place

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "ICO.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="ICO") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))
```

---- 

## Sense of Place: Lasting Special Places

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "LSP.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="LSP") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))

```

---- 


## Biodiversity: Species

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "SPP.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="SPP") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))

```

---- 

## Biodiversity: Habitats

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "HAB.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- layers_csv %>%
  filter(targets=="HAB") %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st$info, collapse="\n\n"))

```

